---
title: "RMarkdown Template"
author: "Author"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    toc_depth: 4
    keep_md: true
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(digits = 4, scipen = 2)
```



# Tidyposterior

<br><br>

Since Accuracy is based on a continuous response, we calculate the intraclass correlation (ICC). All websites were
rated by both coders, so Interrater reliability (IRR) was assessed using a two-way mixed, average-measures ICC [@mcgraw1996forming] to assess the degree that raters (or coders) provided consistency in their ratings of number of incorrect statements across websites. 


```{r}
# devtools::install_github("tidymodels/tidyposterior")

```



```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```


<br> <br>

# Session Info

```{r}
devtools::session_info()
```

<br> <br>

# References
