---
title: "Binomial Frequentist Lasso+Multitask Regression"
author: "by Sahir Bhatnagar"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: false
    number_sections: true
    toc_depth: 4
    keep_md: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 7)
options(digits = 4, scipen = 2)

knitr::read_chunk(here::here("analysis/bin/analysis.R"))
```


# Site as fixed effect

Here I produce the coefficient plots for the logistic lasso regression with glmnet [@R-glmnet]. 



```{r load-data}
```



```{r make-design}
```


## Variable Selection

```{r fit-lasso}
```


## Prediction Performance

Here I provide the prediction performance. Likely overfit because the training set is also used as the test set. 

```{r prediction-performance}
```





# Multitask Lasso

The Objective function for the multitask lasso is given by:

$$
\min\limits_{W, C} \sum_{i=1}^{t}{L(W_i, C_i |X_i, Y_i)} + \lambda ||W||_1 
$$

where $L(\circ)$ is the logistic loss function, $||W||_1$ is the $\ell_1$-norm penalty term on the regression coefficients $W$, $X=\{X_i= n_i \times p | i \in \{1,...,t\}\}$ are the covariates and texture features, $Y=\{Y_i=n_i \times 1 | i \in \{1,...,t\}\}$ is the binary response (Nodal Stage). $W \in \mathbb{R}^{p \times t}$ is the coefficient matrix where $W_i$ is the i$th$ column of $W$ and refers to the coefficient vector of task $i$. $C_i$ is the intercept for task $i$.   



```{r multi-task}

```




```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('glmnet'), file = here::here("analysis/report/bibliography.bib"))
```


<br> <br>

# Session Info

```{r}
devtools::session_info()
```

<br> <br>

# References
