---
title: "Binomial Frequentist Lasso Regression on Texture Features only"
author: "by Sahir Bhatnagar"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    toc_depth: 4
    keep_md: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 7)
options(digits = 4, scipen = 2)

knitr::read_chunk(here::here("analysis/bin/analysis.R"))
```

Here I produce the equivalent coefficient plots for the logistic lasso regression with glmnet [@R-glmnet]. There are mainly two ways to select the tuning parameter. I present both, which is based on 10-Fold cross validation. 


```{r load-data}
```



```{r make-design}
```

# Variable Selection

```{r fit-lasso}
```


# Prediction Performance

Here I provide the prediction performance. Likely overfit because the training set is also used as the test set. 

```{r prediction-performance}
```




```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('glmnet'), file = here::here("analysis/report/bibliography.bib"))
```


<br> <br>

# Session Info

```{r}
devtools::session_info()
```

<br> <br>

# References
